\section{Building blocks}%
\label{Primitives}\label{BuildingBlocks}

\dots

\subsection{Zero-knowledge proofs}

Briefly describe zero-knowledge proofs and what type of properties can be proved 
efficiently using them, e.g.\ algebraic structures but not one-way functions.

\dots

\subsection{Location proofs and distance bounding}

Briefly describe location proofs and distance bounding protocols.
Describe the different desirable properties for distance bounding:
\begin{itemize}
  \item Mafia-fraud resistance,
  \item terrorist-fraud resistance,
  \item impersonation-fraud resistance,
  \item distance-fraud resistance.
\end{itemize}

\subsection{Storage}

We will use the storage to provide the temporal eligibility property.
\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
  set}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
} of objects.
If some objects in the set relate to known points in time, then the partial 
order relates the data to the time of the event.
This allows us to \emph{verify the data temporally}.
One primitive that fulfils these requirements is a blockchain.
There are also other structures, e.g.\ a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
properties.
However, we will use the blockchain in our discussion for simplicity.

There are three properties that we need from the storage system.
The first property we need is decentralized, immutable storage with a general 
form of time-stamping.
I.e.\ once we commit something to the blockchain it will remain there and we do 
not have to trust any central authority.
We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
block appears approximately every 10 minutes.

The second property we need is an unpredictable number whose time of publication 
can be verified.
For this property, we will use the head of the blockchain.
The hash value of the head of the blockchain at a given time will be difficult 
to predict ahead of time.
%(See \cref{SecurityAnalysis} for a security analysis.)
We want to use this to ensure that proofs are created after a certain point in 
time.

The third property is that once we have committed some data, we do not need to 
keep the data itself, but we can store some confirmation value instead.
E.g.\ using blockchains, we can store the hash of the block where our data was 
committed, while this block remains we are sure that our data remains committed 
--- even if we no longer remember what our data looked like.
We will use this property to approximate the property of receipt freeness.

