\subsection{Verifiability requirements}%
\label{verifiability-properties}

We note that, in general terms, protesting is very similar to petitions, which in turn are similar to voting.
Indeed, all three situations correspond to situations in which many individuals express their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
(We discuss privacy in \cref{privacy-properties}.)

We draw inspiration from the three traditionally desired properties for verifiability for voting:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must 
include temporal\footnote{%
  Elections also have some temporal aspects, such that one cannot vote at any 
  time and a vote in one election should not be reusable in the next election.
  However, the temporal relation for a protest is not as strictly defined as for 
  elections as a protest can start at any time and last for an arbitrary period 
  of time.%
}
\seb{the starting and ending time of the protest could also be included in the 
  manifest if we wanted to}
\daniel{Yes, but it's not a requirement.}
and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

To adapt these properties to the context of protests, we define three verifiability requirements, among which eligibility can be further broken up into four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
    \item\label{CountOnce} \emph{Counted only once}: prove that no individual 
      can be counted more than once for a particular protest.
      \seb{this property seems to be related to the eligibility property in the 
        sense that if a participant tries to submit a second proof this 
        directly conflicts with the eligibility}
      \daniel{Yes, that's why it's a sub-property of eligibility, we're trying 
        to make eligibility more concrete.}
    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.
    \end{requirements}

  \item\label{UniversalVerif} \emph{Universal verifiability}: anyone can verify that the result obtained match the submitted participation proofs.

  \item\label{IndividualVerif} \emph{Individual verifiability}: each participant can verify that his participation proof is included in the global count.
\end{requirements}

